Approximate Bayesian Computation in Large Scale Structure: constraining the galaxy-halo connection

### 2017-03-09 ccppabc/text/revision/main.tex
Edits to address Ref Report comment 2, 3 (issues #15 and #17); @mjvakili see issue #22

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). 
}
{\bf \color{darkgreen}
CHH: Need a sentence here that reiterates that the Gaussian functional form 
assumption is incorrect for 2PCF.
}
{\bf \color{dred}
In the case where the observable $\gmf(N)$ is used as a summary statistic
of a galaxy catalog, assuming a Gaussian functional form for the likelihood
clearly misrepresents the true likelihood function. This incorrect likelihood, 
may explain why the constraints on $\alpha$ are less biased for the ABC-PMC analysis 
than the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}

>>>>

{\bf \color{dred}
Furthermore, {\em ABC-PMC -- unlike the Gaussian pseudo-likelihood approach -- 
is agnostic about the functional form of the underlying distribution of the 
summary statistics} (\emph{e.g.} $\xigg$ and $\gmf$). As we explain throughout 
the paper, the likelihood function in LSS {\em cannot} be Gaussian. For $\xigg$, 
the correlation function must satisfy non-trivial positive-definiteness requirements 
and hence the Gaussian pseudo-likelihood function assumption is not correct 
in detail. In the case $\gmf(N)$ is used as a summary statistic
of a galaxy catalog, assuming a Gaussian functional form for the likelihood
clearly misrepresents the true likelihood function. In fact, this incorrect 
likelihood, may explain why the constraints on $\alpha$ are less biased for 
the ABC-PMC analysis than the Gaussian-likelihood analysis in \ref{fig:cont_nbargmf}.
}
{\bf \color{darkgreen}
CHH: @MJV, I parrot a lot of arguments made in the intro without providing much extra 
'meat'. Let me know what you think. 
}
